Estimation of the effect of a continuous treatment variable

### 2025-08-28 Writing/manuscript_CF_continuous.qmd
Adding citations

To identify causal effects rather than just predict levels in the single binary treatment case, researchers use double/debiased machine learning (DML), which introduces orthogonalization so the treatment-effect estimator is insensitive to small errors in the auxiliary fits (I need citation here). 
Consider the structural model (Model 1):

>>>>

To identify causal effects rather than just predict levels in the single binary treatment case, researchers use double/debiased machine learning (DML), which introduces orthogonalization so the treatment-effect estimator is insensitive to small errors in the auxiliary fits (@chernozhukov2018double; @mackey2018orthogonal). 
Consider the structural model (Model 1):
